---
output: github_document
---


```{r, include=FALSE}
tmp <- packageDescription("dratful")
```

```{r, results='asis', echo=FALSE}
cat("#", tmp$Title)
```


**Version**

```{r, results='asis', echo=FALSE}
cat(tmp$Version)
```


**Description**

```{r, results='asis', echo=FALSE}
cat(tmp$Description)
```


**License**

```{r, results='asis', echo=FALSE}
cat(tmp$License)
```


**Installation**

(stable) developement versions: 

```{r, eval=FALSE}
install.packages("dratful", repos = "https://petermeissner.github.io/drat/")
```

**Putting packages into your repository (your own CRAN, your drat, ...)**

The following will:

- check the package using `devtools::check()`
- then (if no errors and warnings were produced) build it into a temporary directory using `devtools::build()`
- then insert it into the drat repo (defaults to `~/git/drat`) using `drat::insertPackage()`



```{r, eval=FALSE}
dratful::drat()
```

If less defaults and more fine control is needed `check_build_publish()` is a version of drat that allows to manipulate options for all three wrapped up fucntions. 


**Getting packages from a drat repository**

While you can install packages from drat repositories as shown in the install section (using the repos option of `install.packages()`) or add repositories  by using `drat::addRepo()` the dratful package offers an alternative way in line with devtools' install functions. 

The following snippet showcases `install_drat`  which takes a package name and a Github user name to use a Github hosted package repository as additional source for packages:

```{r, eval=FALSE}
dratful::install_drat("dratful", "petermeissner")
```











